Spin canonical divisors of log stacky curves

### 2015-06-29 stacky_write_up/spin_cring.tex
sco(L)^... to \lfloor dL \rfloor, more bkgnd items

\todo{Peter: I think we need something about odd weight modular forms before going right into stacks.}  
Following Voight and Zureick-Brown \cite{vzb:stacky}, we generalize Petri's theorem in many \todo{Peter: not clear to me that ``many'' is a good word to use here.  We mostly generalize in one direction}
directions. 
If $X$ is a curve, \todo{why do you start with a curve and then move to a stacky curve? shouldn't it be the opposite order?} then we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$ and {\bf stacky points} $P_1,\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{\geq 2}$ if 
$$\di \sx = \di X \oplus \left(\bigoplus_{i
= 1}^r \left\langle \frac{1}{e_i}P_i \right\rangle \right) \subset \BQ \otimes \di X.$$
As is done in Voight and Zureick-Brown \cite{vzb:stacky} one may view a stacky curve as a stack, but for the purposes of this paper, it suffices to view $\sx$ as a scheme whose associated divisor group allows a finite number of ``fractional points,'' i.e., stacky points. A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where $\Delta \in \di X$ is an effective divisor and $2\halfcan = K_X + \Delta + \sum_{i=1}^{r}\subhalf{e_i}P_i.$
The central object of study in this paper is the {\bf log spin
canonical ring} of $(\sx,\Delta,L)$ is
\begin{align*}
	R(\sx,\Delta,L) = \bigoplus_{d \geq 0} H^0(\sx,\sco(L)^{\otimes d})
\end{align*}

@@

\begin{align*}
	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, \sco(L)^{\otimes d})
\end{align*}

@@

\todo{canonical divisor?}
The pairs $(\sx, \Delta)$ are called \textbf{log stacky curves}
and the study of their canonical rings is the main focus of
the work by Voight and Zureick-Brown \cite{vzb:stacky}.
For this paper, we consider \textbf{log spin curves} which are
triples $(\sx, \Delta, \halfcan)$ where $\Delta$ is a log divisor
and a divisor $\halfcan$ which satisfies the property that
$2\halfcan \sim K_\sx + \Delta$. Such a divisor $\halfcan$
is called a \textbf{half-canonical divisor} on $(\sx, \Delta)$
and are sometimes referred to as theta-characteristics in other
literature. We also use $\halfcan_X$ to refer to the half-canonical
divisor associated with the coarse space $X$ of $\sx$, where
$\halfcan_X$ is a divisor such that $2\halfcan \sim K_X$.
Now we can define the analogy to canonical rings for
log spin curves.

\begin{defn}
The {\bf log spin canonical ring} of $(\sx, \Delta, \halfcan)$ is
\[
	R(\sx, \Delta, L) = \bigoplus_{d \geq 0} H^0(\sx, \sco(L)^{\otimes d})
\]
\end{defn}
\todo{what about floors?}

\noindent
When the log spin curve is fixed, we usually use $R$ to represent
$R(\sx, \Delta, \halfcan)$. We also often use $H^0(\sx, D) :=
H^0(\sx, \sco(D))$ and $h^0(\sx, \sco(D)) := \dim H^0(\sx, \sco(D))$.

@@

\begin{enumerate}
	\item Note that this result is independence of base field
	\item background on Gr\"{o}bner bases
	\item Why we have these fractions $\frac{e_i - 1}{2e_i}$ and why $e_i$ must be odd.
	\item Notation for Gr\"{o}bner bases and orderings (include grlex, grevlex, and block order, as defined in \cite[Definition 8.1.1]{vzb:stacky})
	\item

	\begin{defn}
	\label{def:order-sup}
	If $z$ is a rational section of $\sco(D)$ denote the order of zero of $z$ at $P$ by $\ord_P^D(z)$.
	\item Define $(R_\halfcan)_d$ to refer to the $d^{th}$ component.
	\end{defn}
\end{enumerate}

@@

\begin{thm}
\label{thm:g-1-main}
Let $(\sx, \Delta, \halfcan)$ log spin curve so that $\sx$ has signature $\sigma = (1; e_1, \ldots, e_r; \delta)$.
If $g = 1$, then the canonical ring
\begin{align*}
	R(\sx, \Delta, \halfcan) = \bigoplus_{d = 0}^\infty H^0(\sx, \sco(L)^{\otimes d})
\end{align*}

@@

\begin{align*}
	R(\sx, \Delta, \halfcan) = \bigoplus_{d = 0}^\infty H^0(\sx, \sco(L)^{\otimes d})
\end{align*}

>>>>

\todo{Peter: I think we need something about odd weight modular forms before going right into stacks.}  
Following Voight and Zureick-Brown \cite{vzb:stacky}, we generalize Petri's theorem in many \todo{Peter: not clear to me that ``many'' is a good word to use here.  We mostly generalize in one direction}
directions. 
If $X$ is a curve, \todo{why do you start with a curve and then move to a stacky curve? shouldn't it be the opposite order?} then we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$ and {\bf stacky points} $P_1,\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{\geq 2}$ if 
$$\di \sx = \di X \oplus \left(\bigoplus_{i
= 1}^r \left\langle \frac{1}{e_i}P_i \right\rangle \right) \subset \BQ \otimes \di X.$$
As is done in Voight and Zureick-Brown \cite{vzb:stacky} one may view a stacky curve as a stack, but for the purposes of this paper, it suffices to view $\sx$ as a scheme whose associated divisor group allows a finite number of ``fractional points,'' i.e., stacky points. A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where $\Delta \in \di X$ is an effective divisor and $2\halfcan = K_X + \Delta + \sum_{i=1}^{r}\subhalf{e_i}P_i.$
The central object of study in this paper is the {\bf log spin
canonical ring} of $(\sx,\Delta,L)$ is
\begin{align*}
	R(\sx,\Delta,L) = \bigoplus_{d \geq 0} H^0(\sx,\lfloor d L \rfloor)
\end{align*}

@@

\begin{align*}
	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, \lfloor d L \rfloor)
\end{align*}

@@

The pairs $(\sx, \Delta)$ are called \textbf{log stacky curves}
and the study of their canonical rings is the main focus of
the work by Voight and Zureick-Brown \cite{vzb:stacky}.
For this paper, we consider \textbf{log spin curves} which are
triples $(\sx, \Delta, \halfcan)$ where $\Delta$ is a log divisor
and a divisor $\halfcan$ which satisfies the property that
$2\halfcan \sim K_\sx + \Delta$. Such a divisor $\halfcan$
is called a \textbf{half-canonical divisor} on $(\sx, \Delta)$
and are sometimes referred to as theta-characteristics in other
literature. We also use $\halfcan_X$ to refer to the half-canonical
divisor associated with the coarse space $X$ of $\sx$, i.e.
$\halfcan_X$ is a divisor such that $2\halfcan \sim K_X$.
Now we can define the analogy to canonical rings for
log spin curves.

\begin{defn}
The {\bf log spin canonical ring} of $(\sx, \Delta, \halfcan)$ is
\[
	R(\sx, \Delta, L) = \bigoplus_{d \geq 0} H^0(\sx, \lfloor d L \rfloor)
\]
\end{defn}
\todo{what about floors?}

\noindent
When the log spin curve is fixed, we usually use $R$ or $R_L$ to
represent $R(\sx, \Delta, \halfcan)$. We also often use $H^0(\sx, D)
:= H^0(\sx, \sco(D))$ and $h^0(\sx, \sco(D)) := \dim H^0(\sx, \sco(D))$.

@@

\begin{enumerate}
	\item Note that this result is independence of base field
	\item background on Gr\"{o}bner bases
	\item Notation for Gr\"{o}bner bases and orderings (include grlex, grevlex, and block order, as defined in \cite[Definition 8.1.1]{vzb:stacky})
\end{enumerate}

Define $(R)_d$ to refer to the $d^{th}$ component

\begin{defn}
\label{def:order-sup}
If $z$ is a rational section of $\sco(D)$ denote the order of
zero of $z$ at $P$ by $\ord_P^D(z)$.
\end{defn}

\begin{rem}
\label{rem:odd-denom}
Suppose $(\sx, \Delta, L)$ is a log spin curve. Note that
\[
	L = \sum_{i = 1}^{r} \frac{e_i - 1}{2e_i} P_i + \sum_{i = 1}^{s} a_i P_i
\]

\noindent
where $a_i \in \BZ$ and $e_i$ are odd.
\todo{give reason}
\end{rem}

@@

\begin{thm}
\label{thm:g-1-main}
Let $(\sx, \Delta, \halfcan)$ log spin curve so that $\sx$ has signature $\sigma = (1; e_1, \ldots, e_r; \delta)$.
If $g = 1$, then the canonical ring
\begin{align*}
	R(\sx, \Delta, \halfcan) = \bigoplus_{d = 0}^\infty H^0(\sx, \lfloor d L \rfloor)
\end{align*}

@@

\begin{align*}
	R(\sx, \Delta, \halfcan) = \bigoplus_{d = 0}^\infty H^0(\sx, \lfloor d L \rfloor)
\end{align*}
